Notebook with AMP-AD RNA-seq network analysis results

### 2020-01-03 manuscript.Rmd
updated scripts

>>>>

Run expression weighted cell enrichment method (must have downloaded and unzipped the flat file from GSE97930 in your current working directory: https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE97930&format=file&file=GSE97930%5FFrontalCortex%5FsnDrop%2Dseq%5FUMI%5FCount%5FMatrix%5F08%2D01%2D2017%2Etxt%2Egz )

This step also may require a large compute instance (with > 64 Gb of memory) to successfully run.

```{r}
synapser::synLogin()
g <- AMPAD::run_ewce()
g
```
